Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-07 paper/sec-analysis.tex
analysis section

\subsection{Kinematic distributions}

We now justify some of the cuts that we are using.
%
As mentioned before, the cuts in each category are separately
optimised in an inclusive analysis: it is only we have determined
which is the dominant category that the analysis is made exclusive.
%
We begin with the boosted category.
%
In Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  We see that the background distribution
  falls off rather steeply than the signal, therefore
  suggesting that the boosted region should be
  advantageous to suppress the background.

@@

As explained above, in the boosted category we also require the two
leasing subjets of the large-$R$ jet to be relatively
hard.
%
In Fig ... we show the distribution in $p_T$ of the leading
and subleading jets.
%
It is clear from the comparison that

Let's now consider the resolved category.
%
To begin with, here it is important to understand the $p_T$ distribution
of the four leading small-$R$ jets of the event.
%
Given that in general the boost from the Higgs decays is moderate,
the two subleading jets might be not too hard, and thus it
should be important to ensure that our $p_T^{\rm min}$ cut
is not too strong.
%
In Fig. we show ....

Also, it is useful to show the distribution in rapidity of the
individual jets

Finally, we show in
Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
comparing the resolved category (left) with the boosted category (right)
%
This is interesting since it determines the degree of boost that the two
Higgs candidates will have after non-resonant production.
%
In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the MVA in the next section.
%
For the boosted category the trend of the $m_{hh}$ distribution
is very different because of the selection, with the
distribution now peaking at much higher values.
%
In this case signal and background distributions
look reasonably similar.

>>>>

\subsection{Cut optimisation}

In this section we motivate the various
kinematical cuts for the various categories.
%
As mentioned before, the cuts in each category have been separately
optimised in an inclusive analysis: it is only once we have determined
which is the dominant category that the analysis is made exclusive.
%
In this work, the results for each category have been derived
from the inclusive analysis,
and we show the various kinematic distributions immediately
below the corresponding cut has been applied.

In this section we only show a representative subset of
all available kinematic distributions, the complete
set of comparison plots can be found in the following
webpage:
\begin{center}
\url{http://www2.physics.ox.ac.uk/HH4b}
  \end{center}
In this webpage we also show the distribution of all
kinematic variables, including jet substructure variables,
which we don't cut explicitly but that are provided as
input to the multivariate analysis.
%
Also, we show here results for the boosted and resolved categories,
a comparison which allows to understand the cuts used for the
intermediate category as well.

\subsubsection{Boosted category}

We begin with the boosted category, which is the one that leads
to a higher signal significance.
%
First of all,
in Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  We see that the background distribution
  falls off rather steeply than the signal, therefore
  suggesting that the boosted region should be
  advantageous to suppress the background.

@@

As explained above, in the boosted category we also require the two
leading subjets of the large-$R$ jet to be relatively
hard, in particular that should satisfy $p_T \ge $ 50 GeV.
%
To motivate this cut, in Fig ... we show the distribution in $p_T$ of the leading
and subleading sub-jets in the leading large-$R$ jet in events
of the boosted category.
%
It is clear from the comparison that the subjet $p_T$ spectrum is
relatively harder in the signal with respect to the background,
motivating our cut.

{\bf missing plots: pt subjet distribution}

\subsubsection{Resolved category}

Let's now consider the resolved category.
%
To begin with, here it is important to understand the $p_T$ distribution
of the four leading small-$R$ jets of the event.
%
Given that in general the boost from the Higgs decays is moderate,
the two subleading jets might be not too hard, and thus it
should be important to ensure that our $p_T^{\rm min}$ cut
is not too strong.
%
In Fig. we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events.
%
We see that the third and four leading jets are relatively soft.
%
Also, it is useful to show the distribution in rapidity of the
individual jets

{\bf missing plots: pt jet distribution, rapidity distribution}

Next, we show in
Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
comparing the resolved category (left) with the boosted category (right)
%
This is interesting since it determines the degree of boost that the two
Higgs candidates will have after non-resonant production.
%
In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the MVA in the next section.
%
For the boosted category the trend of the $m_{hh}$ distribution
is very different because of the selection, with the
distribution now peaking at much higher values.
%
In this case signal and background distributions
look reasonably similar.
